Recommendation Generation for Performance Improvement by using Cross-Organizational Process Mining

### 2015-09-15 1_introduction/introduction.tex
no message

The approach proposed in this study is a four-stage solution and it starts with mining the process models of organizations; followed by performance indicator analysis and then mismatch pattern analysis. Finally recommendation generation stage is undertaken to create learning opportunities for each organization. With this approach it is aimed to help business process management users to focus on the potentially important parts of their business maps. Proposed methodology is implemented in ProM framework \cite{verbeek2010prom} as a set of plugins corresponding for each stage and packaged under the name of \textit{CrossOrgProcMin} and tested on a synthetic and real-life event logs. Performance of methodology is assessed with a defined evaluation metrics for each stage and resulting recommendations are presented to show how this approach helps users to focus on learning opportunities between organizations with a performance improvement potential.

>>>>

The approach proposed in this study is a four-stage solution and it starts with mining the process models of organizations; followed by performance indicator analysis and then mismatch pattern analysis. Finally in the suggestion generation stage, learning opportunities are created for each organization. With this approach it is aimed to help business process management users to focus on the potentially important parts of their business maps. Proposed methodology is implemented in ProM framework \cite{verbeek2010prom} as a set of plugins corresponding for each stage and packaged under the name of \textit{CrossOrgProcMin} and tested on a synthetic and real-life event logs. Performance of methodology is assessed with a set of defined evaluation metrics for each stage and resulting recommendations are presented to show how this approach helps users to focus on learning opportunities between organizations with a performance improvement potential.

### 2015-09-15 2_relatedwork/relatedwork.tex
no message

In this section, studies related to the work presented in this research are summarized. Firstly, studies in the process mining area are explained and then studies from cross-organizational process mining, which is the main topic of this research, is introduced. Following these, studies related to similarity in process mining are presented.

>>>>

In this section, studies related to the presented work are summarized. Firstly, studies in the process mining area are explained and then studies from cross-organizational process mining, which is the main topic of this research, are introduced. Following these, studies related to similarity in process mining are presented.

### 2015-09-15 3_background/background.tex
no message

In this section process discovery methods and mismatch patterns are presented within the  the scope of this resarch and the aim of constructing a necessary background.

In process mining field, various process discovery algorithms are proposed to address different challenges in process discovery and using different notations. However, in this study focus of the study is learning from the cross-organizational process mining rather than addressing all process discovery challenges. With this reasoning, Inductive Process Mining \cite{leemans2013discovering} is selected as appropriate since it is simple, highly applicable and configurable. In the literature, its derivatives which handles infrequent behaviors \cite{leemans2014discoveringinfrequent}; incomplete logs \cite{leemans2014discoveringincomplete}; and model optimization \cite{weidlich2012profiles} are also available. \textit{Inductive Miner Infrequent (IMi)} \cite{leemans2014discoveringinfrequent} extension is used in this study which is capable of filtering the infrequent behavior and results with lower fitness, higher precision and equal generalization.

In cross-organizational process mining environment, there is a need to align processes of different organizations and in this scope both the organizations and their processes are similar but have significant differences. In order to align these processes and organizations, there is a need for spotting differences between process models. In the study of Dijkman \cite{dijkman2007mismatch}, a collection of patterns to describe frequent mismatches between the similar process models are presented. Within the scope of this study, the related mismatch patterns are defined in study \cite{dijkman2007mismatch} as follows:
\begin{description}
  \item[Skipped Activity] An activity exists in one process but no equivalent activity is found in the other process.
  \item[Refined Activity] An activity exists in one process but, as an equivalent, a collection of activities are existing in the other process to achieve the same task.
  \item[Activities at Different Moments in Processes] Set of activities are undertaken with different orders in different processes.
  \item[Different Conditions for Occurrence] Set of dependencies are same for two processes; however, occurrence condition is different.
  \item[Different Dependencies] Dependency set of activities differ in different organizations.
  \item[Additional Dependencies] This pattern is a special case of different dependencies where one set of activities includes the other and results with additional dependencies.
\end{description}

As mentioned in the study \cite{dijkman2007mismatch}, their approach does not create a comprehensive list to resolve all mismatches but the most common ones spotted during case studies. In addition, from their definitions and examples it can be easily seen that these patterns are not orthogonal. Moreover, there are no algorithms provided to spot these mismatches in \cite{dijkman2007mismatch} or consequent studies, and thus implementation of spotting mismatch patterns are kept within the scope of this study.

>>>>

In this section, process discovery methods and mismatch patterns are presented within the scope of this work. In process mining field, various process discovery algorithms are proposed to address different challenges in process discovery and using different notations. In this study, since the focus is learning lessons from cross-organizational mining, we used Inductive Process Mining \cite{leemans2013discovering} for process discovery, which is simple, highly applicable and configurable. In the literature, its derivatives which handles infrequent behaviors \cite{leemans2014discoveringinfrequent}; incomplete logs \cite{leemans2014discoveringincomplete}; and model optimization \cite{weidlich2012profiles} are also available. \textit{Inductive Miner Infrequent (IMi)} \cite{leemans2014discoveringinfrequent} extension is used in this study which is capable of filtering the infrequent behavior and results with lower fitness, higher precision and equal generalization.

In cross-organizational process mining environment, there is a need to align processes of different organizations. In order to align these processes and organizations, a mechanism is needed for spotting differences between process models. In the study of Dijkman \cite{dijkman2007mismatch}, a collection of patterns to describe frequent mismatches between the similar process models are presented. Within the scope of this study, the related mismatch patterns are defined in study \cite{dijkman2007mismatch} as follows:
\begin{description}
  \item[Skipped Activity] An activity exists in one process but no equivalent activity is found in the other process.
  \item[Refined Activity] An activity exists in one process but, as an equivalent, a collection of activities are existing in the other process to achieve the same task.
  \item[Activities at Different Moments in Processes] Set of activities are undertaken with different orders in different processes.
  \item[Different Conditions for Occurrence] Set of dependencies are same for two processes; however, occurrence condition is different.
  \item[Different Dependencies] Dependency set of activities differ in different organizations.
  \item[Additional Dependencies] This pattern is a special case of different dependencies where one set of activities includes the other and results with additional dependencies.
\end{description}

As mentioned in the study \cite{dijkman2007mismatch}, their approach does not create a comprehensive list to resolve all mismatches but includes the most common mismatch patterns spotted during case studies. In addition, from their definitions and examples it can be easily seen that these patterns are not orthogonal. Moreover, there are no algorithms provided to spot these mismatches in \cite{dijkman2007mismatch} or consequent studies, and thus implementation of spotting mismatch patterns are performed within the scope of this study.

### 2015-09-15 4_methodology/methodology.tex
no message

\subsection{Process Model Mining}
\label{subsec:process-model-mining}
Process model mining in the proposed approach has the aim of creating reproducible and generalized process models from event logs. In order to achieve this aim, implementation of \textit{Inductive Miner Infrequent (IMi)}, which is proposed in \cite{leemans2014discoveringinfrequent} as an extension to \textit{Inductive Miner} to handle noise in the event logs, is used in this study. In order to set a filtering threshold, a user-provided value between 0 to 1 is added as input to method in addition to event logs. Black-box of this stage is illustrated in Figure~\ref{fig:process-model-mining-blackbox} and this stage is called for every organization's event logs to create their own process models in Workflow net formalization.
\begin{figure}
  \centering
  \includegraphics[width=0.5\textwidth]{4_methodology/process-model-mining-blackbox}
  \caption{Process Model Mining Stage as Black-box }
  \label{fig:process-model-mining-blackbox}
\end{figure}

\subsection{Performance Indicator Analysis}
\label{subsec:performance-indicator-analysis}
Performance indicator analysis stage focuses on calculating and analyzing the performance values using the event logs and mined process models. This stage consists of mainly two concepts as 
\begin{inparaenum}[\itshape a\upshape)]
\item alignment and calculation of performance indicators; and
\item clustering of organizations based on their performance values.
\end{inparaenum}
In order to evaluate the performance of an organization based on their process models and past activities; there is a number of indicators in time dimension, cost dimension and utilization \cite{van2011process}. However, in this study, process related performance values are considered since differences in the process models are studied in the next stages. With this reasoning, the following performance indicators are calculated and analyzed in this stage of methodology:
\begin{description}
	\item[Average Time Between Activities] For each activity in the process model, average time to reach other activity is calculated. This is a simple but powerful performance metric for organizations since it can yield the average time to complete one task based on a starting point. From the performance perspective, organizations want to minimize average time between activities to increase their throughput \cite{van2012replaying}.
	\item[Standard Deviation of Time Between Activities] Time between activities in real life is not stable and they deviate due to various reasons such as people responsible of tasks, size and the content of tasks or seasonality \cite{van2011process}. On the other hand, organizations want to be confident about their processes and therefore they want to minimize the deviation in the time between activities. Minimized deviation in time helps organizations to plan, act and re-organize the activities in the processes with high accuracy \cite{van2012replaying}. 
\end{description}

\subsubsection{Replay and Performance Indicator Calculation}
\label{subsubsec:replay-and-performance-summary}
Replay of event logs on process models is based on the idea of \textit{alignment} which is formalized in \cite{van2012replaying} and the basic assumption in this concept is that process models and event logs have the same activity labels. For each organization, the steps alignment and creating transitions are undertaken with the corresponding event logs and process models; and the resulting process summaries are used for further analysis.

\subsubsection{Performance Indicator Clustering}
\label{subsubsec:performance-indicator-clustering}
Clustering is based on the idea of collecting the set of observations into clusters so that observations within the same cluster are similar whereas the observations from different clusters are dissimilar. In this study, clustering is used to gather organizations based on their performance indicator data. In this research, random initialization based \textit{k-means++} approach from the study of Arthur and Vassilvitskii \cite{arthur2007} is used to cluster organizations. Since number of clusters are not known priori, k-means clustering is applied starting \textit{k} from 1 to the number of organizations. For each clustering with different number of clusters, SSE values are plotted and user is made to select the appropriate cluster size. For the selected cluster size, clustering related information is used to generate recommendations in the further steps. This stage of methodology can be visualized as an input-output system in Figure~\ref{fig:performance-indicator-clustering-blackbox}. 
\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{4_methodology/performance-indicator-clustering-blackbox}
  \caption{Performance Indicator Clustering Stage as Black-box }
  \label{fig:performance-indicator-clustering-blackbox}
\end{figure}

\subsection{Mismatch Pattern Analysis}
\label{subsec:mismatch-pattern-analysis}
In order to learn from other organizations, it is necessary to spot the differences between process models of different organizations. In this phase of methodology, differences between process models will be revealed by the mismatch patterns which are defined by Dijkman \cite{dijkman2007mismatch}. In the process mining stage, process models are mined to create Workflow nets; however, mismatch pattern definitions are closer to business environment and it is more suitable spot patterns in BPMN notation. Thus, mined process models are converted to BPMN models and then mismatch pattern analysis is applied in order to locate differences between two process models or cluster of process models. In addition, since performance indicators are calculated based on a starting and ending points in the process model, same approach is applied to locate mismatch patterns. In other words, differences of process models are located through a starting activity to an ending activity. For each organization, mismatch patterns are gathered and stored for the further analysis as visualized in Figure~\ref{fig:mismatch-pattern-analysis-blackbox}.
\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{4_methodology/mismatch-pattern-analysis-blackbox}
  \caption{Mismatch Pattern Analysis Stage as Black-box}
  \label{fig:mismatch-pattern-analysis-blackbox}
\end{figure}

\subsection{Recommendation Generation}
\label{subsec:recommendation-generation}
Recommendation generation stage in the methodology is the final and core stage where all information retrieved from event logs until now are utilized. In this study, idea of recommendation is based on providing a set of mismatch patterns for each organization so that they can enhance their processes. These mismatch patterns are generated by comparing the process models of other organizations, particularly which are performing better in terms of their performance indicator values. In addition, clustering of organizations is undertaken to generalize the way of identifying which organizations perform better in this environment.

Algorithm of recommendation generation function is based on the idea of checking other clusters for a significant change in performance indicators, where significance is defined by the threshold provided by user. After finding significant difference, all organizations in other clusters are checked against mismatch patterns with the starting and ending activities defined in performance indicators. With this constraining, only mismatches which are located between the activities that causes high level of difference in performance indicators are analyzed.

This stage of methodology can be visualized as gathering inputs of mismatch patterns data and cluster analysis data in Figure~\ref{fig:recommendation-generation-blackox}. In addition, a performance difference threshold is gathered from the user to specify how much difference between clusters is necessary to check for mismatch patterns and generate recommendations. This stage generates recommendation data for each organization which contains a set of mismatch patterns.
\begin{figure}
  \centering
  \includegraphics[width=0.5\textwidth]{4_methodology/recommendation-generation-blackbox}
  \caption{Recommendation Generation Stage as Black-box}
  \label{fig:recommendation-generation-blackox}
\end{figure}

>>>>

\subsection{Process Model Mining}
\label{subsec:process-model-mining}
Process model mining in the proposed approach has the aim of creating reproducible and generalized process models from event logs. In order to achieve this aim, implementation of \textit{Inductive Miner Infrequent (IMi)}, which is proposed in \cite{leemans2014discoveringinfrequent} as an extension to \textit{Inductive Miner} to handle noise in the event logs, is used in this study. In order to set a filtering threshold, a user-provided value between 0 to 1 is added as input to the method in addition to event logs. Black-box of this stage is illustrated in Figure~\ref{fig:process-model-mining-blackbox} and this stage is called for every organization's event logs to create their own process models in Workflow net formalization.
\begin{figure}
  \centering
  \includegraphics[width=0.5\textwidth]{4_methodology/process-model-mining-blackbox}
  \caption{Process Model Mining Stage as Black-box }
  \label{fig:process-model-mining-blackbox}
\end{figure}

\subsection{Performance Indicator Analysis}
\label{subsec:performance-indicator-analysis}
Performance indicator analysis stage focuses on calculating and analyzing the performance values using the event logs and mined process models. This stage consists of mainly two steps as 
\begin{inparaenum}[\itshape a\upshape)]
\item alignment and calculation of performance indicators; and
\item clustering of organizations based on their performance values.
\end{inparaenum}
In order to evaluate the performance of an organization based on their process models and past activities; there is a number of indicators in time dimension, cost dimension and utilization \cite{van2011process}. However, in this study, process related performance values are considered since differences in the process models are studied in the next stages. To this aim, the following performance indicators are calculated and analyzed in this stage of methodology:
\begin{description}
	\item[Average Time Between Activities] For each activity in the process model, average time to reach the next activity is calculated. This is a simple but powerful performance metric for organizations since it can yield the average time to complete one task based on a starting point. From the performance perspective, organizations want to minimize average time between activities to increase their throughput \cite{van2012replaying}.
	\item[Standard Deviation of Time Between Activities] Time between activities in real life is not stable and they deviate due to various reasons such as the user responsible of tasks, size and the content of tasks or seasonality \cite{van2011process}. On the other hand, organizations want to be confident about their processes and therefore they want to minimize the deviation in the time between activities. Minimized deviation in time helps organizations to plan, act and re-organize the activities in the processes with high accuracy \cite{van2012replaying}. 
\end{description}

\subsubsection{Replay and Performance Indicator Calculation}
\label{subsubsec:replay-and-performance-summary}
Replay of event logs on process models is based on the idea of \textit{alignment} which is formalized in \cite{van2012replaying} and the basic assumption in this concept is that process models and event logs have the same activity labels. For each organization, the steps of alignment and creating transitions are performed with the corresponding event logs and process models; and the resulting process summaries are used for further analysis.

\subsubsection{Performance Indicator Clustering}
\label{subsubsec:performance-indicator-clustering}
Clustering is based on the idea of collecting the set of observations into clusters so that observations within the same cluster are similar whereas the observations from different clusters are dissimilar. In this study, clustering is used to gather organizations based on their performance indicator data. In this research, random initialization based \textit{k-means++} approach from the study of Arthur and Vassilvitskii \cite{arthur2007} is used to cluster organizations. Since the number of clusters are not known priori, k-means clustering is applied starting \textit{k} from 1 to the number of organizations. For each clustering with different number of clusters, SSE values are plotted and user is asked to select the appropriate cluster size. For the selected cluster size, clustering related information is used to generate recommendations in the further steps. This stage of methodology can be visualized as an input-output system in Figure~\ref{fig:performance-indicator-clustering-blackbox}. 
\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{4_methodology/performance-indicator-clustering-blackbox}
  \caption{Performance Indicator Clustering Stage as Black-box }
  \label{fig:performance-indicator-clustering-blackbox}
\end{figure}

\subsection{Mismatch Pattern Analysis}
\label{subsec:mismatch-pattern-analysis}
In order to learn from other organizations, it is necessary to spot the differences between process models of different organizations. In this phase, differences between process models will be revealed by the mismatch patterns which are defined by Dijkman \cite{dijkman2007mismatch}. In the process mining stage, process models are mined to create Workflow nets; however, mismatch pattern definitions are closer to business environment and it is more suitable spot patterns in BPMN notation. Thus, mined process models are converted to BPMN models and then mismatch pattern analysis is applied in order to locate the differences between two process models or two clusters of process models. In addition, since performance indicators are calculated based on a starting and ending point in the process model, the same approach is applied to locate mismatch patterns. In other words, differences of process models are located through a starting activity to an ending activity. For each organization, mismatch patterns are gathered and stored for the further analysis as visualized in Figure~\ref{fig:mismatch-pattern-analysis-blackbox}.
\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{4_methodology/mismatch-pattern-analysis-blackbox}
  \caption{Mismatch Pattern Analysis Stage as Black-box}
  \label{fig:mismatch-pattern-analysis-blackbox}
\end{figure}

\subsection{Recommendation Generation}
\label{subsec:recommendation-generation}
Recommendation generation stage in the methodology is the final and core stage where all information retrieved from event logs until now are utilized. In this study, idea of recommendation is based on providing a set of mismatch patterns for each organization so that they can enhance their processes. These mismatch patterns are generated by comparing the process models of other organizations, particularly those that are performing better in terms of their performance indicator values. In addition, clustering of organizations is undertaken to generalize the way of identifying which organizations perform better in this environment.

Algorithm of recommendation generation function is based on the idea of checking other clusters for a significant change in performance indicators, where significance is defined by the threshold provided by user. After finding significant difference, all organizations in other clusters are checked against mismatch patterns with the starting and ending activities defined in performance indicators. Only mismatches which are located between the activities that causes high level of difference in performance indicators are analyzed.

This stage of methodology can be visualized as gathering inputs of mismatch patterns data and cluster analysis data in Figure~\ref{fig:recommendation-generation-blackox}. In addition, a performance difference threshold is gathered from the user to specify how much difference between clusters is necessary to check for mismatch patterns and generate recommendations. This stage generates recommendation data for each organization that contains a set of mismatch patterns.
\begin{figure}
  \centering
  \includegraphics[width=0.5\textwidth]{4_methodology/recommendation-generation-blackbox}
  \caption{Recommendation Generation Stage as Black-box}
  \label{fig:recommendation-generation-blackox}
\end{figure}

### 2015-09-15 5_results_discussions/loan-application-process/loan-application-process.tex
no message

\subsection{Loan Application Process}
\label{subsec:loan-app-process}
\textit{Loan Application Process} dataset is synthetically created and consists of four variants of a simple loan application in a financial institute. These event logs are used to test different approaches of discovering a configurable process model from a collection of event logs \cite{buijs2014flexible}. In this dataset there are a total of 475 cases and 2440 events with a fairly even distribution between variants and these variants are used as organizational logs and the methodology presented in this study is be applied.

>>>>

\subsection{Loan Application Process}
\label{subsec:loan-app-process}
\textit{Loan Application Process} dataset is synthetically created and consists of four variants of a simple loan application in a financial institute. These event logs are used for testing different approaches of discovering a configurable process model from a collection of event logs \cite{buijs2014flexible}. In this dataset there are a total of 475 cases and 2440 events with a fairly even distribution between variants and these variants are used as organizational logs and the methodology presented in this study is be applied.

### 2015-09-15 5_results_discussions/results_discussions.tex
no message

In this section, methodology presented in this study is applied on datasets and results are presented. Firstly, evaluation metrics are defined for each stage of methodology to assess the performance of approach. Following this, methodology is applied on two datasets and results are explained with discussions.

@@

	\item Recommendation generation aims to gather all generated information in this study to help focusing on the potentially important mismatch patterns for performance improvement. When the number of mismatch patterns with and without performance clusterings are checked, it shows that in a small dataset performance clustering lists 3 times less number of differences in \textit{Loan Application Example} dataset. When it is impossible to locate mismatch patterns manually like in \textit{Environmental Permit Application Process}, performance clustering spots 100 times less number of differences. This difference helps user to focus on the differences with a potential performance improvement which is one of the aims in this thesis study.

>>>>

In this section, methodology presented in this study is applied on several data sets and results are presented. Firstly, evaluation metrics are defined for each stage of methodology to assess the performance of approach. Following this, methodology is applied on two data sets and results are explained with discussions.

@@

	\item Recommendation generation aims to gather all generated information in this study to help focusing on the potentially important mismatch patterns for performance improvement. When the number of mismatch patterns with and without performance clusterings are checked, it shows that in a small dataset performance clustering lists 3 times less number of differences in \textit{Loan Application Example} dataset. When it is impossible to locate mismatch patterns manually like in \textit{Environmental Permit Application Process}, performance clustering spots 100 times less number of differences. This difference helps user to focus on the differences with a potential performance improvement which is one of the aims in this study.

### 2015-09-15 paper.tex
no message

@@

\title{Recommendation Generation for Performance Improvement by using Cross-Organizational Process Mining}
%If Title is too long, use \titlerunning
%\titlerunning{Short Title}

%Single insitute
\author{Onur Yilmaz \and Pinar Karagoz}
%If there are too many authors, use \authorrunning
%\authorrunning{First Author et al.}
\institute{Computer Engineering Department, Middle East Technical University, Turkey}
%\email{yilmaz.onur@metu.edu.tr} 
%\email{karagoz@ceng.metu.edu.tr}
%Multiple insitutes
%Currently disabled
%
\iffalse
%Multiple institutes are typeset as follows:
\author{Firstname Lastname\inst{1} \and Firstname Lastname\inst{2} }
%If there are too many authors, use \authorrunning
%\authorrunning{First Author et al.}

@@

\begin{abstract}
Process mining is a relatively young and developing research area with the main idea of discovering, monitoring and improving processes by extracting information from the event logs. With the increase of cloud computing and shared infrastructures, event logs of multiple organizations are available for analysis where cross-organizational process mining stands with the opportunity for organizations learning from each other. The approach proposed in this study mines process models of organizations and calculates performance indicators; followed by clustering of organizations based on performance indicators and finally spots mismatches between the process models to generate recommendations. This approach is implemented as extensible and configurable plugin set in ProM framework and tested by synthetic and real life logs where successful and suitable results are achieved within evaluation metrics. Generated recommendation results indicate that the use of this approach considerably helps users to focus on the areas of process models with potential performance improvement, which are difficult to spot manually and visually.
\end{abstract}

\keywords{Process Mining, Cross-organizational Process Mining, Recommendation Generation, Process Performance Improvement}

\input{1_introduction/introduction.tex}

\bibliographystyle{splncs03}
\bibliography{references/references}

>>>>

\usepackage{url}

@@

\title{Recommendation Generation for Performance Improvement by using Cross-Organizational Process Mining}
%If Title is too long, use \titlerunning
\titlerunning{Cross-Organizational Process Mining}

%Single insitute
\author{Onur Yilmaz \and Pinar Karagoz}
%If there are too many authors, use \authorrunning
%\authorrunning{First Author et al.}
\institute{\email{\{onur.yilmaz, karagoz\}@ceng.metu.edu.tr} \\ Computer Engineering Department, Middle East Technical University, Turkey}
%\email{karagoz@ceng.metu.edu.tr}
%Multiple insitutes
%Currently disabled
%
\iffalse
%Multiple institutes are typeset as follows:
\author{Firstname Lastname\inst{1} \and Firstname Lastname\inst{2} }
%If there are too many authors, use \authorrunning
%\authorrunning{First Author et al.}

@@

\begin{abstract}
Process mining is a relatively young and developing research area with the main idea of discovering, monitoring and improving processes by extracting information from the event logs. With the increase of cloud computing and shared infrastructures, event logs of multiple organizations are available for analysis where cross-organizational process mining stands with the opportunity for organizations learning from each other. The approach proposed in this study mines process models of organizations and calculates performance indicators; followed by clustering of organizations based on performance indicators and finally spots mismatches between the process models to generate recommendations. This approach is implemented as extensible and configurable plugin set in ProM framework and tested by synthetic and real life logs where successful and suitable results are achieved within evaluation metrics. Generated recommendation results indicate that the use of this approach can help users to focus on the areas of process models with potential performance improvement, which are difficult to spot manually and visually.
\end{abstract}

\keywords{Process Mining, Cross-organizational Process Mining, Performance Indicators, Clustering, Process Performance Improvement}

\input{1_introduction/introduction.tex}
\input{2_relatedwork/relatedwork.tex}
\input{3_background/background.tex}
\input{4_methodology/methodology.tex}
\input{5_results_discussions/results_discussions.tex}
\input{6_conclusion_future_work/conclusion_future_work.tex}

\bibliographystyle{splncs03}
\bibliography{7_references/references}
